A re-examination of the role of friction in the original Social Force Model

### 2019-05-20 paper.tex
reemplace ki y kw por k en la figura 9

\textcolor{red}{In the last decades many microscopic models 
for crowd dynamics have been develop. One of the first model was developed by Hirai 
and Tarui (1975) introducing the class of \textit{force based} models 
\cite{Hirai}. These models represents the interaction between 
pedestrians and their environment through different kinds of forces. For 
example, Okazaki (1979) simulated the movement of each pedestrian by the motion 
of a magnetized object in magnetic field which exerts attractive force on the 
different kind of magnetic poles \cite{Okazaki}.}\\

@@

\textcolor{blue}{By the late '90s and the beginning of the century, Helbing and 
co-workers postulated that both the environment and the individuals' own desire 
affect the pedestrians motion in a similar way as forces do with respect to the 
momentum of particles \cite{Helbing1,Helbing4}. This ``Social Force Model'' 
(SFM) nicely bridged the socio-psychological phenomenon of crowds 
behavior to the ``microscopic'' formalism of moving particles. The model 
succeeded at this instance to explain why the crowd evacuation slows down 
as pedestrians try harder to escape from a dangerous situation 
(\textit{i.e.} ``faster is slower'' effect) \cite{Helbing1,Dorso1,Dorso2}.} \\

@@

It is well known that the \textcolor{red}{original} version of the Social Force 
Model \textcolor{red}{\cite{Helbing1}} is incapable of reproducing the 
fundamental diagram at high densities (say above 
\textcolor{red}{5~p~m$^{-2}$)}. Different 
approaches were proposed to fix this drawback: increasing the net-time 
headway~\cite{johansson}, canceling the desired velocity~\cite{parisi2} or even 
inducing the jamming state by an attraction target~\cite{kwak}. These approaches 
seems suitable when individuals are not so anxious to reach a certain 
destination. However, when individuals are escaping or rushing due to a 
stressful situation, pedestrians would neither consider reducing their desired 
force nor being captured by an attraction. \\

\begin{figure}[htbp!]
\centering
\includegraphics[width=0.7\columnwidth]
{./corridor.eps}
\caption{\label{corridor} Schematic diagram for individuals in the corridor. 
The circles represent pedestrians moving from left to right. $w$ represents the 
corridor width, $L$ represents the length. The rectangular boxes are upper and 
lower blocks that represent the walls of the corridor. The dashed circle in the 
middle corresponds to the measurement region.}
\end{figure}

@@

As we mentioned in Section \ref{fundamental_diagram}, when the density is low, pedestrians achieve the desired velocity ($v=v_d=1$~m/s). Since the results of the previous Section only hold for the area located in the middle of the corridor (see Fig.~\ref{corridor}), we want to shed some light and understand what is happening across the entire corridor.\\

>>>>

\textcolor{red}{In the last decades, many microscopic models 
for crowd dynamics have been developed. One of the first models was developed by Hirai 
and Tarui (1975) introducing the class of \textit{force based} models 
\cite{Hirai}. These models represent the interaction between 
pedestrians and their environment using different kinds of forces inspired in physical systems. For 
example, Okazaki (1979) modeled the movement the pedestrians as the motion 
of a magnetized object within a magnetic field \cite{Okazaki}.}\\

@@

@@

It is well known that the \textcolor{red}{original} version of the Social Force 
Model \textcolor{red}{\cite{parisi2}} is incapable of reproducing the 
fundamental diagram at high densities (say above 
\textcolor{red}{5~p~m$^{-2}$)}. Different 
approaches were proposed to fix this drawback: increasing the net-time 
headway~\cite{johansson}, canceling the desired velocity~\cite{parisi2} or even 
inducing the jamming state by an attraction target~\cite{kwak}. These approaches 
seems suitable when individuals are not so anxious to reach a certain 
destination. However, when individuals are escaping or rushing due to a 
stressful situation, pedestrians would neither consider reducing their desired 
force nor being captured by an attraction. \\

\begin{figure}[htbp!]
\centering
\includegraphics[width=0.7\columnwidth]
{./corridor.eps}
\caption{\label{corridor} Schematic diagram for individuals in the corridor. 
The circles represent pedestrians moving from left to right. $w$ represents the 
corridor width, $L$ represents the length. The rectangular boxes are upper and 
lower blocks that represent the walls of the corridor. The dashed circle in the 
middle corresponds to the \textcolor{red}{fundamental diagram} measurement region.}
\end{figure}

@@

As we mentioned in Section \ref{fundamental_diagram}, when the density is low, pedestrians achieve the desired velocity ($v=v_d=1$~m/s). Since the results of the previous Section only hold for the area located in the middle of the corridor (see \textcolor{red}{dashed circle in} Fig.~\ref{corridor}), we want to shed some light and understand what is happening across the entire corridor.\\
